Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex
Filled out the table and edited section 2.1

@@

KEPID

@@

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets'' on exoplanets.org

@@

GAMMA\dotfill & & Systemic radial velocity in k\mps & -UPPER, etc. \\

@@

SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$

@@

SEDEPTHKP\dotfill & & Secondary eclipse depth in the

@@

SEDEPTH36\dotfill & & Secondary eclipse depth in

@@

SEDEPTH45\dotfill & & Secondary eclipse depth in

@@

SEDEPTH58\dotfill & & Secondary eclipse depth in

@@

SEDEPTH80\dotfill & & Secondary eclipse depth in

@@

SET\dotfill & & Epoch of secondary eclipse center in

>>>>

We report basic planet information to give our users general information of when, by whom and how the planets were discovered. Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.

@@

KEPID: For KOIs, the Exoplanet Archive reports Kepler ID.

@@

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets'' on exoplanets.org

@@

GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\

@@

SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & Float & Secondary eclipse depth in $K_S$

@@

SEDEPTHKP\dotfill & Float & Secondary eclipse depth in the

@@

SEDEPTH36\dotfill & Float & Secondary eclipse depth in

@@

SEDEPTH45\dotfill & Float & Secondary eclipse depth in

@@

SEDEPTH58\dotfill & Float & Secondary eclipse depth in

@@

SEDEPTH80\dotfill & Float & Secondary eclipse depth in

@@

SET\dotfill & Double & Epoch of secondary eclipse center in
